---
title: "Assignment 1.3 : R Refresher"
author: "Gourav Verma"
date: "Sept 05 2020"
output: 
  html_document:
    df_print: paged
  word_document: default
  pdf_document: default
---

```{r, echo=FALSE, message=FALSE}

setwd("C:/Users/f4puslg/Desktop/Garv/ML/Term 7 - Predictive Analysis/Assignments")

library(ggplot2)

```
***
#### **Que 1: Using the Bureau of Labor Statistics data, choose a dataset that interest you. Then generate summary statistics for 2 variables, plot some of the features (e.g., histograms, box plots, density plots, etc.) of several variables, and save the data locally as CSV files.**

##### ==> Read the CSV File from Bureau of Labor Statistics
```{r}
OES <- read.csv("OES_data_M_2019.csv")
```
\

##### ==> summary statistics for 2 variables
##### **tot_emp:**	Estimated total employment rounded to the nearest 10 (excludes self-employed).
```{r}
summary(as.numeric(OES$tot_emp))
```

##### **a_mean:**	Mean annual wage 
```{r}
summary(as.numeric(OES$a_mean))
```
\

##### ==> plot some of the features
##### **Histogram of area_type**. Area type: 1= U.S.; 2= State; 3= U.S. Territory; 4= Metropolitan Statistical Area (MSA) or New England City and Town Area (NECTA); 6= Nonmetropolitan Area 
```{r}
hist(OES$area_type)
```
\

##### **Box plot of annual mean wage**
```{r}
boxplot(as.numeric(OES$a_mean), main='Annual mean wage', ylab="mean Wage")
```
\

##### **Density plot of Ownership type**
##### Ownership type: 1= Federal Government; 2= State Government; 3= Local Government; 123= Federal, State, and Local Government; 235=Private, State, and Local Government; 35 = Private and Local Government; 5= Private; 57=Private, Local Government Gambling Establishments (Sector 71), and Local Government Casino Hotels (Sector 72); 58= Private plus State and Local Government Hospitals; 59= Private and Postal Service; 1235= Federal, State, and Local Government and Private Sector 
```{r}
d <- density(as.numeric(OES$occ_code))
plot(d, main="Ownership type")
polygon(d, col="red", border="blue")
axis(side=1,at=OES$own_code)
```
\


##### **Density plot**
```{r}
ggplot(OES, 
       aes(x = as.numeric(OES$a_mean), 
           fill = o_group)) +
    geom_density(alpha = 0.4) +
    labs(title = 'Salary distribution') +
    xlab("Annual Mean Salary")
```
\

##### **Density plot**
```{r}
AT <- as.factor(OES$area_type)  
ggplot(OES, 
       aes(x = as.numeric(OES$a_mean), 
           fill = AT)) +
    geom_density(alpha = 0.4) +
    labs(title = 'Salary distribution for Area Type') +
    xlab("Annual Mean Salary")
```
\

##### **Write into CSV file**
```{r}
write.csv(OES, "OES_new.csv")
```
***

#### **Que 2:** Explore Some Bivariate Relations
##### **Scatter plot between annual mean wage and PRSE error**
```{r, message=FALSE, warning=FALSE}
plot(as.numeric(OES$a_mean), as.numeric(as.character(OES$mean_prse)), main="scatter plot", 
     xlab="annual mean wage", ylab="Percent relative standard error (PRSE) for wage")
```

***
#### **Que 3:** Organize a Data Report
##### The default CSV read takes the datatypes automatically. For furhter analysis datatype conversion is required.
##### a. **Area Type** is a categorical field with 5 distinct values. 
+ 1 = U.S.
+ 2 = State
+ 3 = U.S. Teritory
+ 4 = Metropolitan Statistical Area (MSA) or New England City and Town Area (NECTA)
+ 6 = Nonmetropolitan Area
\
 
##### b. **OCC code and Title** are categorical fields which contains code and title of occupation. 
##### c. **h_mean and a_mean** are float variables which represents hourly and Annual mean wage respectively for perticular job code in the area type.
##### d. **Ownership code** is a categorical variable for type of ownership of the occupation title.
Ownership type: 
+ 1= Federal Government; 
+ 2= State Government; 
+ 3= Local Government; 
+ 123= Federal, State, and Local Government; 
+ 235=Private, State, and Local Government; 
+ 35 = Private and Local Government; 
+ 5= Private; 
+ 57=Private, Local Government Gambling Establishments (Sector 71), and Local Government Casino Hotels (Sector 72); 
+ 58= Private plus State and Local Government Hospitals; 
+ 59= Private and Postal Service; 
+ 1235= Federal, State, and Local Government and Private Sector
\
 
##### Below is the summary of the datatet
```{r}
str(OES)

```